%DO NOT MESS AROUND WITH THE CODE ON THIS PAGE UNLESS YOU %REALLY KNOW WHAT YOU ARE DOING
 \chapter{Preparation}

\section{Discrete white noise }
\noindent \textbf{Task:} Specify the constant component, the covariance function and the spectral density of discrete white noise.\\
\noindent \textbf{Solution:}\\




%**************section 2********
\section{Generation of AR(\textit{p})-processes}
\noindent \textbf{Task:} Make oneself familiar with the MATLAB-function \texttt{filter.} The function \texttt{filter} is used for the generation of an AR($p$)-process. Which values have to be entered for the filter coefficient vector \textbf{b}? Which value has to be assigned to the first element $a_0$ of the filter coefficient vector \textbf{a}?\\
\noindent \textbf{Solution:}\\




%**************section 3********
\section{LS-Estimation}
\noindent \textbf{Task:} How can one determine the least squares estimates of the parameters $a_1 , a_2 ,..., a_p ;{\sigma_z}^2$ for the given observations $x_i ( i = 1,2,...,N )$? How large has to be the number of observations $N$? How large must be $N$, if the estimates shall be determined by solving the empirical Yule-Walker-Equations?
\\
\noindent \textbf{Solution:}\\




%**************section 4********
\section{LS-Estimation}
\noindent \textbf{Task:} Which particular property of the coefficient matrix of the following Yule-Walker-Equation system
\begin{equation*}
\begin{pmatrix}
c_{xx}(0) & c_{xx}(1) & ... & c_{xx}(p-1)\\
c_{xx}(1) & c_{xx}(0) & ... & c_{xx}(p-2)\\
. & . &.  &. \\
. & . &\;\;.  &. \\
. & . &\; \; \; \; .  &. \\
c_{xx}(p-1) & c_{xx}(p-2) & ... & c_{xx}(0)\\
\end{pmatrix}
\begin{pmatrix}
a_1\\
a_2\\
. \\
. \\
. \\
a_p \\
\end{pmatrix} = -
\begin{pmatrix}
c_{xx}(1)\\
c_{xx}(2)\\
. \\
. \\
. \\
c_{xx}(p)\\
\end{pmatrix}
\end{equation*}
permits the application of the Levinson-Durbin-Algorithm? Is the Levinson-Durbin-Algorithm be suited for solving the equation system of the LS-Estimation procedure? Give reasons for your answer. Which advantage offers the Levinson-Durbin-Algorithm with respect to the model order estimation? How can the model order be estimated? \\
\noindent \textbf{Solution:}\\